Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-19 main.tex
Updates from Overleaf

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective 
  way to probe the electroweak sector of the Minimal Supersymmetric 
  Standard Model (MSSM). In this paper, we describe a search strategy  
  for discovering pair-produced Higgsino-like NLSPs  at a 100 TeV 
  hadron collider that decay to Bino-like LSPs via intermediate Z and 
  SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
  $b$-quarks respectively: $\N_{2,3}\N_{3,2}
  \rightarrow (Z\N)(h\N)\rightarrow 
  bbll+\N\N$. In addition, we examine 
  the potential for machine learning techniques to boost the power of 
  our searches. Using this analysis, Higgsinos up to 1.3 TeV can be 
  discovered for Binos  up to 0.9 TeV using 3000 fb$^{-1}$ of data,  
  Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
  to 1.3 TeV at 95\% C.L. \\

  \noindent \Shufang{Abstract need to be more detailed.  Let's worry about this after we
  get the draft done.   } \\
}

@@

The existence of dark matter provides unambiguous evidence of new 
physics beyond the Standard Model (SM) of particle physics. Indeed, 
given that there is far more dark matter in the Universe than there 
is baryonic matter, determining its precise nature is one of the most 
exciting challenges in particle physics today.  One promising group 
of candidate for dark matter is the class of stable particles known as 
weakly interacting massive particles (WIMPs). These particles arise 
naturally in many extensions of the SM that are motivated by the need to
stabilize the electroweak scale. One of the most studied extensions
to the SM is the Minimal Supersymmetric Standard Model
(MSSM), which predicts a `supersymmetric partner', or \emph{superpartner}, 
for each SM particle\footnote{For a detailed review of the MSSM, see 
Ref. \citep{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the 
lightest supersymmetric partner (LSP) is predicted to be absolutely 
stable, making it a good candidate for dark matter. The identity of 
the LSP is determined by the mass hierarchy of the superpartners, 
which in turn depends on how supersymmetry is broken.
However, taking into account experimental constraints and phenomenological 
considerations, the lightest of the  MSSM particles known as the 
neutralinos emerges as the most attractive candidate for the LSP \citep{Bertone:2004pz}.

% Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
this limit is from the disappearing track search - does that apply for us?} The
limits on electroweakinos,
howeer, are still relatively weak: around 0.3 $-$ 1.1 \Adarsh{I'm rounding 1150
GeV down to 1.1 TeV - is that ok?}
TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae} \Adarsh{0.15
- 1.1 if we include the gravitino analysis}, depending on
the decay modes of the parent electroweakinos.  \Shufang{add ref for 
electroweakino limits. Fill in the number.} In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

% Point to review papers for enumeration of studies
The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos)
depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
roughly determine the masses of the Bino, Winos, and Higgsinos, respectively.
In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
One of the motivations for studying Higgsinos is that the parameter $\mu$ 
that governs its mass plays an important role in electroweak symmetry breaking 
\citep{Acharya:2014pua}. Finding Higgsinos has traditionally been more challenging 
than finding Winos, due to their lower production rate. This, however, can 
be remedied by the increased  production cross sections and luminosities 
at a 100 TeV collider.

Since the Bino is the only supersymmetric particle lighter than the Higgsino in
the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a
neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
Higgsinos with intermediate gauge boson and multi-lepton final states have been
studied in Ref.~\cite{Gori:2014oua}. \Shufang{Add more details for that study.
Which channel, search resutls, etc. This would be our comparison for our
analyses.} \Adarsh{These details are already in section 2 (page 3) - should I
repeat them here?}  In this paper we attempt to exploit the relatively high branching
ratio of the SM Higgs boson to \emph{b} quarks, and study the decay mode
$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.

% Why a 100 TeV collider?
A 100 TeV collider would open up an immense number of physics
opportunities not afforded to a 14 TeV collider, including exploring the
most interesting regions of the split SUSY parameter space
\citep{Arkani-Hamed:2015vfh}.
% Status of 100 TeV planning
Such a collider would be a natural next step after the LHC, and is being
actively discussed in the particle physics community, with two major
proposals being the FCC-hh by CERN \citep{FCC-hh}, and the SppC  
in China \citep{CEPC}.  As the next energy frontier machine, it is of 
crucial importance to fully explore the physics potential of a 100 TeV $pp$
collider, especially for new particles that are either too heavy or too rare 
to be produced at the LHC~\citep{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
In particular, studies have already been performed on the prospects of
discovering neutralino dark matter for compressed \cite{Low:2014cba, diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}
and well-separated \cite{Gori:2014oua,Acharya:2014pua}
neutralino spectra.

We use razor variables~\citep{Rogan:2010kb} in our study, which were originally designed
for searches involving two heavy, mass-degenerate pair-produced
particles, each of which decays into a visible and invisible set of
particles. This topology matches that of our search channel, making this
set of variables a natural choice for our analysis.

At a 100 TeV collider, the backgrounds are going to be even larger than
at the LHC.  An ancillary goal of this paper is to investigate the
potential for machine learning (ML) techniques to augment our analysis.
With the advent of more powerful computers and simultaneous advances in
the field of statistical learning in recent years, the usage of ML is
rising in experimental particle physics - in fact, the discovery of the
SM Higgs boson in 2012 was done with the help of neural networks
\citep{Aad:2012tfa} and boosted decision trees (BDT)
\citep{Chatrchyan:2012xdj}.

The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we describe our model and search channel in more
detail, and list the existing experimental constraints on it. In Sec.~\ref{sec:analysis}, we describe our analysis strategies 
for both traditional cut-and-count analyses and analyses
performed using BDT. In Sec.~\ref{sec:results},
we present the results of our analyses, i.e. the expected discovery and exclusion
reaches. Finally, we conclude with the implications in Sec.~\ref{sec:conclusion}.

@@

\[\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & -\sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},\]

\Shufang{Check.  I think this matrix goes with
($\B,\widetilde{W}^0,\H_d,\H_u$). \Adarsh{Good catch - I have fixed it.}}
\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as
$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

@@

The optimal search strategy for finding electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
believe I've already addressed this with the paragraphs I added below in response
to your comment ... let me know if I should add more details.}.
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form

\begin{align}
  pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
  \met,
\end{align}

\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the lower pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{2}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 16 fb\\
    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
    Applying \emph{BR}$(W\rightarrow l\nu)$, \emph{BR}$(Z\rightarrow ll)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{2})$ and
    $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
    TeV \emph{pp} collider . The pair-production cross sections are taken from
    \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
    evaluated in the limit where the Goldstone equivalence theorem applies, so
    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_{1}^0)\approx$
    BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_1^0)\approx 50\% $,
    and the branching ratios to the SM final states are taken from
    \citep{Olive:2016xmw}. \ap{In this scenario, the LSP is assumed to be
    massless}.
    \Shufang{Specify M1 as well and use the actual Br.} \Adarsh{I added a line
  specifying that the LSP is massless. As for the actual BR, I assume you mean
  calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
  get it.}\Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
  \Adarsh{$\chi_1$ is the LSP, right? In our case it's the bino, which is not
  charged...}
  \label{tab:xsections}
\end{table}

@@

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production
cross section for the Higgsino-like NLSPs.  The cross section varies between
200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
While one of the Higgsinos mostly decays to $Z$, the other
Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative
discovery channel for Higgsinos.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production cross section, as a function of $|\mu|$. The
  cross-sections are calculated using Prospino2, with $M_1 = 25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.  
  \Shufang{Could you make the two plot same aspect ratios?}}
  \Adarsh{It would be pretty time consuming to do, so I would rather not if
    it's not essential - I think it might look better to put the plots in
  separate figures.}
  \label{fig:xsection_plot}
\end{figure}

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay  topologies. While the identity of
the LSP in these searches is a gravitino  instead of a Bino,   the limits are
still  relevant, since both  our analysis  and the experimental ones consider
that  the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the
LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP
  and Bino LSP case.} \Adarsh{True, but there have been no experimental
  searches for Higgsino NLSP - Bino LSP. This seemed like the most similar
channel/topology to ours.}

The most stringent limits are obtained by ATLAS in \cite{Aaboud:2018htj},
where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
GeV are excluded using a search channel with a final state containing at least
three \emph{b}-jets. \Shufang{you mean more than 3 b jets?} \Adarsh{At least 3 -
I've reworded to clarify.} The CMS analysis
in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
$4b+\slashed{E}_T, 2l + 2j + \slashed{E}_T, 3l/4l + \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
to exclude Higgsino-like neutralino masses up to 650-750 GeV, depending on the assumed branching 
fraction of the neutralino decays. Finally, the $4l$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
\Shufang{So the only available limit is with gravitino LSP?  Then it does not apply.}
\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?} \Adarsh{Yes, that is the
only available limit with neutral Higgsino NLSPs and bino LSP, and with
on-shell W and Z. WZ+MET limits (with on-shell W and Z). Should I remove the
sentences with the gravitino LSP?}.

@@

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \citep{Alwall:2014hca}, then passed those events to Pythia 6
\citep{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \citep{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2} \citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
Wino, we set its mass parameter $M_2$ to 5 TeV. \Shufang{5 TeV was used for
another calculation earlier. Be consistent here.}

>>>>

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective 
  way to probe the electroweak sector of the Minimal Supersymmetric 
  Standard Model (MSSM). In this paper, we describe a search strategy  
  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles  at a 100 TeV 
  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP) via intermediate $Z$ and 
  SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
  $b$-quarks respectively: $\N_{2}\N_{3}
  \rightarrow (Z\N)(h\N)\rightarrow 
  bbll+\N\N$. In addition, we examine 
  the potential for machine learning techniques to boost the power of 
  our searches. Using this analysis, Higgsinos up to 1.3 TeV can be 
  discovered for Binos  up to 0.9 TeV using 3000 fb$^{-1}$ of data,  
  Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially at large LSP mass region. \Shufang{Update the numbers.}
}

@@

The existence of dark matter provides unambiguous evidence of new 
physics beyond the Standard Model (SM) of particle physics. Indeed, 
given that there is far more dark matter in the Universe than there 
is baryonic matter, determining its precise nature is one of the most 
exciting challenges in particle physics today.  One promising group 
of candidate for dark matter is the class of stable particles known as 
weakly interacting massive particles (WIMPs). These particles arise 
naturally in many extensions of the SM that are motivated by the need to
stabilize the electroweak scale. One of the most studied extensions
to the SM is the Minimal Supersymmetric Standard Model
(MSSM), which predicts a `supersymmetric partner', or \emph{superpartner}, 
for each SM particle\footnote{For a detailed review of the MSSM, see 
Ref. \citep{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the 
lightest supersymmetric partner (LSP) is predicted to be absolutely 
stable, making it a good candidate for dark matter. The identity of 
the LSP is determined by the mass hierarchy of the superpartners, 
which in turn depends on how supersymmetry is broken.
However, taking into account experimental constraints and phenomenological 
considerations, the lightest of the  MSSM particles known as the 
neutralinos emerges as the most attractive candidates for the LSP \citep{Bertone:2004pz}.

 % Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
this limit is from the disappearing track search - does that apply for us? Update - disappearing tracks not relevant, use the regular channel} \Shufang{Actually on a second thought, in split SUSY with heavy squarks, is the gluino lifetime long enough to leave displaced vertex at detectors? Check pheno of split SUSY paper. If still decay promptly, then use searches with off-shell squark.} The
limits on electroweakinos,
howeer, are still relatively weak: around 0.3 $-$ 1.1 
TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae}, depending on
the decay modes of the parent electroweakinos.  \Shufang{add ref for 
electroweakino limits.  Again, for searches with heavy squark/sleptons.} In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

% Point to review papers for enumeration of studies
The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos)
depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
roughly determine the masses of the Bino, Winos, and Higgsinos, respectively~\citep{Han:2013kz}. 
In this paper, we consider the Higgsino next-to-LSP (NLSP) and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
One of the motivations for studying Higgsinos is that the parameter $\mu$ 
that governs its mass plays an important role in electroweak symmetry breaking~\citep{Acharya:2014pua}, which tends to be small by naturalness considerations.   Finding Higgsinos has traditionally been more challenging 
than finding Winos, due to their smaller production rate. This, however, can 
be remedied by the increased  production cross sections and luminosities 
at a 100 TeV $pp$ collider.

Since the Bino is the only supersymmetric particle lighter than the Higgsino in
the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a
neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been
studied in Ref.~\cite{Gori:2014oua} for 100 TeV $pp$ collider, for pair production of $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm$ and  $\widetilde\chi_{1}^+\widetilde\chi_1^-$.    In this paper, we attempt to exploit the relatively high branching
ratio of the SM Higgs boson to \emph{b} quarks, and study the potential of the channel of
$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.

% Why a 100 TeV collider?
A 100 TeV $pp$ collider would open up an immense number of physics
opportunities not afforded to a 14 TeV LHC, including exploring the
most interesting regions of the split SUSY parameter space
\citep{Arkani-Hamed:2015vfh}.
% Status of 100 TeV planning
Such a collider would be a natural next step after the LHC, and is being
actively discussed in the particle physics community, with two major
proposals being the Future Circular Collider (FCC)-hh by CERN \citep{FCC-hh}, and the Super Proton Proton Collider (SppC)  
in China \citep{CEPC}.  As the next energy frontier machine, it is of 
crucial importance to fully explore the physics potential of a 100 TeV $pp$
collider, especially for new particles that are either too heavy or too rare 
to be produced at the LHC~\citep{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
In particular, studies have already been performed on the prospects of
discovering neutralino dark matter for compressed \cite{Low:2014cba, diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}
and well-separated \cite{Gori:2014oua,Acharya:2014pua}
neutralino spectra.

In our study, we use razor variables~\citep{Rogan:2010kb}, which were originally designed
for searches involving two heavy, mass-degenerate pair-produced
particles, each of which decays into a visible and invisible set of
particles. This topology matches that of our search channel, making this
set of variables a natural choice for our analysis.

At a 100 TeV collider, the  SM backgrounds are going to be even larger than
at the LHC.  An ancillary goal of this paper is to investigate the
potential for machine learning (ML) techniques to augment our analysis.
With the advent of more powerful computers and simultaneous advances in
the field of statistical learning in recent years, the usage of ML is
rising in experimental particle physics -- in fact, the discovery of the
SM Higgs boson in 2012 was done with the help of neural networks
\citep{Aad:2012tfa} and boosted decision trees (BDT)
\citep{Chatrchyan:2012xdj}.

The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we describe our model and search channel in more
detail, and list the existing experimental search bounds. In Sec.~\ref{sec:analysis}, we describe our analysis strategies 
for both traditional cut-and-count analyses and analyses
performed using BDT. In Sec.~\ref{sec:results},
we present the results of our analyses, i.e. the expected 5 $\sigma$ discovery and 95\% C.L. exclusion
reaches. Finally, we conclude with the implications in Sec.~\ref{sec:conclusion}.

@@

\begin{equation}
\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & -\sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},
\end{equation}
where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as
$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

@@

The optimal search strategy for finding electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
believe I've already addressed this with the paragraphs I added below in response
to your comment ... let me know if I should add more details.}. \Shufang{What you said below is for well separated spectra, not for mass spitting of 0.1 to 50 GeV.}
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{align}
  pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2\ell/3\ell +  
  \met,
\end{align}
where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino,
$\widetilde{\chi}_1^0$ is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$ or scalar $h$.  These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.  Higgsino NLSPs can be excluded at 95\% C.L. with mass up to 2.85 TeV or be discovered with  mass up to 1.8 TeV, for massless Bino LSP.   The reach reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).    Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the smaller pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 16 fb\\
    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
    Applying \emph{BR}$(W\rightarrow \ell\nu)$, \emph{BR}$(Z\rightarrow \ell\ell)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of Higgsino pair production cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
    $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
    TeV \emph{pp} collider. The pair-production cross sections are taken from
    \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
    evaluated in the limit where the Goldstone equivalence theorem applies, so
    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow Z \widetilde{ \chi}_{1}^0)\approx$
    BR$(\widetilde{\chi}_{2,3}^0\rightarrow h\widetilde{\chi}_1^0)\approx 50\% $ for massless $\widetilde{\chi}_{1}^0)$, 
    and the branching ratios to the SM final states are taken from
    \citep{Olive:2016xmw}.  
    \Shufang{use the actual Br.} \Adarsh{As for the actual BR, I assume you mean
  calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
  get it.} \Shufang{You can read the number out from right panel of Fig. 2.} }
  \label{tab:xsections}
\end{table}

@@

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
While one of the Higgsinos mostly decays to $Z$, the other
Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative
discovery channel for Higgsinos.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\citep{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.   \Shufang{How about Br? What's the vcalue of M1 used?}\\
  \Shufang{Could you make the two plot same aspect ratios? Using plot digitizer.  Also, for ylabel in left panel, the tilde should not go above 0.  Just above $\chi$.  Is there way to change the xlabel of right panel to be $\mu$ instead of $|\mu|$?  Need to be consistent with the xlabels.}}
  \label{fig:xsection_plot}
\end{figure}

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay  topologies. While the identity of
the LSP in these searches is a gravitino  instead of a Bino,   the limits are
still  relevant, since both  our analysis  and the experimental ones consider
that  the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the
LSP 100\% of the time.

The most stringent limits are obtained by ATLAS in \cite{Aaboud:2018htj},
where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
GeV are excluded using a search channel with a final state containing at least
three \emph{b}-jets.  \Shufang{Check the ref.  The mass windows seem a bit weird.  Is one for Higgsino and the other one for Bino?}  The CMS analysis
in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
$4b+\slashed{E}_T, 2\ell + 2j + \slashed{E}_T, 3\ell/4\ell+ \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
to exclude Higgsino-like neutralino masses up to 650 $-$ 750 GeV, depending on the assumed branching 
fraction of the neutralino decays. Finally, the $4\ell$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
\Shufang{Check, finalize}

@@

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \citep{Alwall:2014hca}, then passed those events to Pythia 6
\citep{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \citep{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2}~\citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
Wino, we set its mass parameter $M_2$ to 5 TeV.

Since we expect our signal process to have a dilepton resonance from an on-shell
$Z$ boson, we restricted the phase space for event generation for backgrounds to
the region where the invariant mass of dilepton pairs lies between 80 and 100
GeV. Additionally, the Bino dark matter that escapes the detector would result
in a large amount of missing transverse energy ($\met$), so we required
a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
well.  \Shufang{This is only for BG, right?  No such cuts are imposed for signal generation?}
